Glyph-maps for visualizing climate data and models

### 2011-09-23 paper.tex
perception section

Compare the facetted map Figure \ref{facetted-map} with the glyph-map
of de-seasonalized data in Figure \ref{fig:nasa-deseas-glyph}.

Glyph-maps using trend lines enable the reading of trends across
spatial locations directly from the plot. In comparison, to read trend
from facetted colored maps one needs to spot the difference between
the different maps. A more direct comparison would be to make a single
map with the slope of the trend coded as color. Cleveland's
\citep{cleveland:1993a} perceptual tests suggests that the reader can
perceive the positional difference of the lines better than the color
differences. Accurate perception of color differences is difficult.

\begin{figure*}[htp]
\centerline{\includegraphics[width=6in]{nasa-deseas-glyph.png}}
\caption{Glyph-map of de-seasonalized temperature, to compare with Figure \ref{facetted-map}. }
\label{fig:nasa-deseas-glyph}
\end{figure*}

>>>>

Glyph-maps using trend lines enable the reading of trends across
spatial locations directly from the plot. In comparison, to read trend
from facetted colored maps one needs to spot the difference between
the different maps.  Compare the facetted map in Figure
\ref{fig:facetted-map} with the glyph-map of de-seasonalized data in
Figure \ref{fig:nasa-deseas-glyph}. The glyph-map provides a texturing
over the map. The El Ni\~no event is still primary structure, visible
as the region that has a bump in the middle of the time series, the
hot 1997-1998 period. We can also see that the temperatures are
generally more varied over land. There are a few locations with
dramatically increasing temperature in the later years

Another common approach is to compute the slope at each location code
this as color on the map. Cleveland's \citep{cleveland:1993a}
perceptual tests suggests that the reader can perceive the positional
difference of the lines better than the color differences. Accurate
perception of color differences is difficult.

\begin{figure*}[htp]
\centerline{\includegraphics[width=5in]{nasa-deseas-glyph.png}}
\caption{Glyph-map of de-seasonalized temperature, to compare with Figure \ref{fig:facetted-map}. }
\label{fig:nasa-deseas-glyph}
\end{figure*}
